Correcting K-correction: restoring the time dilation term and fixing the inverted zero-point term removes accelerating expansion and resolves the Hubble tension

### 2025-01-04 paper/dark_energy_corrections.tex
Incorporate some suggestions

\shorttitle{Dark energy is based on a math error from 1930}
\shortauthors{Evans}

@@

\title{Dark energy is based on a math error from 1930}

@@

\begin{abstract}
We show that the apparent magnitude of distant objects has been calculated
incorrectly since 1930. We describe how this redshift correction flaw in the
formula for K-corrections has propagated for over nine decades. We also
re-derive the K-corrections equation. This derivation reveals that the
correction for zero-points in different filters also has a flaw. We explore the
consequences of properly correcting apparant magnitudes for redshift and
conclude that this resolves two of the preeminent mysteries in cosmology: dark
energy is not supported by observations of Type Ia supernovae, and the Hubble
tension is due to a calculation error.
\end{abstract}

@@

The measurement of Type Ia supernovae is one of the primary sources of data for
cosmological models. The measurements involve estimating the peak magnitude in
the B filter \citet{riess1998} for the rest frame, meaning we want to know how
bright the SnIa would be if its light did not undergo redshift. Redshift causes
the light that would be measured by the B filter in a rest frame to be shifted
to another filter. In order to observe a SnIa in an arbitrary filter and report
the magnitude in the B filter we use a technique called K-corrections.

The first formal derivation of K-corrections was performed by
\citet{tolman1930} and it failed to account for bandwidth stretching, one of
the dimming effects of redshift. This error was noted by \citet{desitter1934},
but in \citet{hubble1935} the discrepancy was noted and ignored.
\citet{oke1968} rederived K-corrections, but they failed to account for time
dilation, one of the other dimming effects of redshift. In \citet{kim1996},
K-corrections were extended to handle additional cross-filter comparisons and
address zero-point corrections, but they started their derivation by
referencing the incorrect equation from \citet{oke1968}. The derivation in
\citet{kim1996} forms the basis for modern implementations of K-corrections.
This history is explored in more depth in Section \ref{sec:history}.

The effect of using an incorrect magnitude for SnIa is that we think objects
are farther away than they really are, and the effect compounds for greater
distances. Up until \citet{riess1998}, we didn't have distant enough
observations for this error to matter much for cosmology models, but in the
late 1990s, it was clear that our measurements for distance and redshift were
not linear. This observation led to a model that utilized a cosmological
constant and dark energy in order to explain the non-linear distance-redshift
graph. We will show in Section \ref{sec:tension} that correcting the flaw
with K-corrections leads to a linear graph that does not need to rely on a
cosmological constant.

\citet{planck2020} used an alternative technique to compute the Hubble constant
that is based on measurements of the cosmic microwave background. CMB based
computations of $H0$ has made it evident that something was missing with our
understanding of cosmology because this measurement is incompatible with the
Hubble constant when measured from SnIa. As we will discuss in Section
\ref{sec:tension}, fixing the error with K-corrections produces a measurement
of the Hubble constant that is compatible with models based on the cosmic
microwave background.

\section{A brief history of K-corrections}
\label{sec:history}

Observations of Type Ia supernova are essential to calibrate models that
measure redshift and estimate distance. This relationship, often called the
Hubble-Lema\^{i}tre law, describes how quickly the universe is expanding.
However, \citet{riess1998} and \citet{perlmutter1999} presented evidence that
there isn't a linear relationship between redshift and distance, but instead,
distant objects are farther away than their redshift would predict (see Figure
\ref{fig:mu_distance_vs_redshift}). This phenomenon implies that the
acceleration of the universe is faster today than it was for old observations.
Previously the cause of this phenomenon was unknown and was referred to as
dark energy.

@@

Type Ia supernovae are used to explore the relationship between distances and
redshifts because these events always happen in similar ways, so the absolute
brightness is roughly always the same. An analogy is to imagine someone walking
in the dark and lighting matches. As long as we know how brightly a match burns
at a known distance, we can estimate the distance to any match by measuring the
apparent brightness before applying some geometry.

@@

\begin{itemize}
  \item The energy of a wave is inversely proportional to its wavelength, so a
  redshift of $z$ means the amount of energy per photon is reduced by a factor
  of $\frac{1}{1+z}$.

  \item The bandwidth is stretched out. If a rest frame would observe photons
  between teh wavelengths of 400nm and 401nm, then with a redshift of $z = 1$,
  redshifting these photons will spread them across the wavelengths from 800nm
  to 802nm.

  \item Cosmological time dilation reduces the rate at which photons arive.
\end{itemize}

To complicate matters, we use the B-band magnitude to calculate luminosity
distance. We want to know how bright a supernova appears for wavelengths around
445nm as if no redshift had occured. However, we typically need to observe the
supernova with a filter that is sensitive to longer wavelengths, such as the
i-band filter which is sensitive to wavelengths from 700nm-850nm
\citep{flaugher2015}. The K-corrections formula allows us to take a magnitude
measured in an observation filter $y$ and compute the magnitude in the target
filter $y$.

The first mathematical treatments of K-corrections was performed by
\citet{tolman1930}. However, when Tolman made his derivation, he did not
consider the effects of a spectra that is stretched out due to redshift. See
the top two panels of Figure \ref{fig:k-example} for an example of this effect.

@@

A year later, \citet{hubble1935} published a similar set of calculations for
K-corrections, but these equations used $(1 + z)^2$ instead of the $(1 + z)^3$
correction term used by de Sitter. They started their derivation by copying the
incorrect equation from 1930. After their derivation, they noted,

@@

The Hubble K-corrections with the incorrect correction term have been used ever
since.

By \citet{oke1968}, the two factors of $(1 + z)$ were attributed to the change
in energy and to the spectral bandwidth elongation, which leaves time dilation
as the factor that was omitted. A graph that demonstrates why it's essential to
correct for both the spectra bandwidth warping and time dilation is presented
in Figure \ref{fig:k-example}.

\begin{figure}
  \includegraphics[width=.75\linewidth]{K-corrections_for_photon_counts.png}
  \caption{An example of how K-corrections take an observed magnitude and
  produce a rest frame magnitude. In this example, $z=1$. The observation
  filter measures magnitude, which is equivalent to measuring the number of
  photons per nanometer. In the bottom left panel, a correction of $1+z$ is
  applied which doubles the photons per nanometer. The top right panel shows
  the effect of correcting for the bandwidth spectrum warping effect --
  correcting all wavelengths for the rest frame means that the measured
  wavelengths have blueshifted, ideally into the cross band B filter. Applying
  both effects, shown in the bottom right panel, requires applying two
  correction factors of $1+z$. This example omits the correction for a similar
  effect related to lower energy due to the Planck relation because CCD cameras
  obviate the need to correct for this effect.
  }
  \label{fig:k-example}
\end{figure}

The modern treatment of K-corrections is based on the work of \citet{kim1996}.
This work extended the calculations of K-corrections to extend to filters
beyond B and V. It also introduced a term that deals with the zero-point for
the actual filters. In the modern day, filters measure the photon flux as
opposed to the energy flux. Historically, bolometric devices would measure the
energy flux, but modern CCD cameras effectively measure the photon flux.

@@

This equation has three errors, which we will explore in Section
\ref{sec:consequences}.

\section{Derivation of K-corrections}
\label{sec:derivation}

With modern CCD cameras, a telescope observation consists of a single value
$\mathcal{F}_x$ erg/s, which represents the energy collected in filter $x$ per
second. A summary of how this works is provided by \citet{lesser2015}. The
measured energy is produced by electrons not photons, so the measured number is
proportional to the number of photons. However, we need to calculate the
expected number of photons collected by using a spectral energy density
function $F$. The value $F(\lambda)$ gives the amount of energy collected by a
bolometric device for the wavelength $\lambda$.

@@

It's important to note that for the blueshifted wavelength $\lambda / (1+z)$,
this equation produces

@@

  In order to account for this bandwidth spectral warping effect, we will need
  to multiply $F'$ by a second factor of $1/(1+z)$.
\end{itemize}

Combining these two phenomena together, we can calculate the redshifted
spectral energy density $R$ using

@@

Now that we have the identities in Equations \ref{eq:flux_definition} and
\ref{eq:flux2mag} we will change directions and look at the definition of
K-corrections $K_{xy}$. This value allows us to make an observation in filter
$y$ and report what the magnitude would have been in filter $x$ if no redshift
occured:

@@

The second line of Equation \ref{eq:definition} expands the distance modulus
$\mu$ using $\mu = m - M$ where $m$ is the observed magnitude and $M$ is the
absolute magnitude.

@@

It's useful to inspect this equation to consider whether the term
$\frac{P'_y}{P'_x}$ is correct, or if it might be flipped to the inverse of
what it should be. However, if we rewrite Equation \ref{eq:as_flux} as

@@

\noindent then the meaning is a bit more clear. The left hand side
$\mathcal{F}_x \times P'_x$ is the rate of photon collection for an idealized
telescope in filter $x$ while $\mathcal{F}_y \times P'_y$ is the rate of photon
collection for an idealized telescope in filter $y$. We are able to observe the
value $\mathcal{F}_y \times P'_y$ and want to use the fudge factor $K'_{xy}$ to
produce the value $\mathcal{F}_x \times P'_x$.

@@

Now we use Equations \ref{eq:redshifted_density} and \ref{eq:flux_definition}
to calculate the fluxes $\mathcal{F}_x$ and $\mathcal{F}_y$ in terms of the
spectral energy density function $F$. Note that $\mathcal{F}_x$ uses the rest
frame spectral energy density $F$ while $\mathcal{F}_y$ uses the redshifted
spectral energy density $R(\lambda)$:

@@

\noindent where, according to \citet{kim1996}, "$\mathcal{Z}(\lambda)$ is an
idealized spectral energy distribution at $z = 0$ for which
$U = B = V = R = I = 0$ in the photometric system being used." Combining this
with Equation \ref{eq:K2k}, we have

@@

\begin{itemize}
  \item The sign is different for the first term. This will have a subtle but
  frustrating effect for real measurements. Typically the zero-point values are
  similar, so this term is close to 0. However, the term isn't always zero. As
  we observe more distant supernovae, it is useful to switch our observational
  filter to a filter that is sensitive to longer wavelengths. Each observation
  filter will have its own small bias.

  This effect by itself can alter estimates of $H_0$ by several km/s / Mpc.
  While we present an estimate of the Hubble constant in Figure
  \ref{fig:H0bootstrap}, we aren't terribly confident in the numbers because we
  were unable to correct for the zero-point correction errors or verify that
  these errors don't exist.

  \item The second term is multiplied by a $2.5$ in \citet{kim1996} but is
  multiplied by a $5$ here. This is the manifestation of the error in
  \citet{tolman1930}.

  \item In our derivation, the third term is has an extra $1 + z$ expression.
  Based on an inspection of the SN(oo)py software package presented by
  \citet{snpy}, this error is ignored and software package authors implement it
  as the expression is intended, not precisely as the expression is written.
\end{itemize}

@@

Since the corrected values are approximately linear, we can use them to
estimate the Hubble constant $H0$. This is demonstrated in Figure
\ref{fig:expansion}. Furthermore, we performed a bootstrap calculation to
estimate the distribution of $H0$ estimates in Figure \ref{fig:H0bootstrap}.

The value estimated here, $H0 \sim 65.94 \pm 1.29$ is highly suspicious because
of the flipped zero-point corrections, but it is consistent with estimates of
$H0$ that are based on the CMB. \citet{planck2020} published the CMB value of
$H0 \sim 67.27 \pm 0.6$, and the one sigma error bars overlap. It is
interesting to note that restricting the DES observations to only those with $z
< 0.1$, which presumably is a small enough redshift that all observations will
have been made with the same filter, gives the estimate
$H0 \sim 67.8 \pm 1.86$.

@@

\begin{figure}
  \includegraphics[width=\linewidth]{bootstrapped_H0.png}
  \caption{A histogram of 100000 bootstrap trials measuring the Hubble constant
  $H0$. Each trial samples an absolute Type Ia magnitude $M \sim Norm(-19.2334,
  0.0404)$ based on data published by \citet{camarena2020}. It then samples,
  with replacement, a population of supernovae from the dataset published by
  \citet{abbott2024}. Finally, it uses the non-parametric linear regression
  technique described by \citet{siegel1982}. The result of the bootstrap is $H0
  \sim Norm(65.94, 1.29^2)$.
  }
\label{fig:H0bootstrap}
\end{figure}

@@

A lot of data is going to have to be reanalyzed.

>>>>

\shorttitle{Correcting K-correction}
\shortauthors{Evans}

@@

\title{Correcting K-correction: restoring the time dilation term and fixing the
inverted zero-point term removes accelerating expansion and resolves the Hubble
tension}

@@

\begin{abstract}
We rederive the K-correction equation and discover that the version of the
equation used in modern cosmology contains three errors. The oldest of these
errors traces back nine decades; in 1930 the equation did not correct for
spectral bandwidth stretching, followed by a rederivation in 1968 that
accounted for spectral bandwidth stretching but did not correct for time
dilation. Two new errors were introduced in 1996, one of which causes
systematic distance biases by inverting the zero-point correction term. We
conclude that properly correcting apparent magnitudes for redshift resolves two
of the preeminent mysteries in cosmology: first, dark energy is not supported
by observations of Type Ia supernovae and second, the Hubble tension is due to
the errors in the K-correction equation.
\end{abstract}

@@

The estimate of Type Ia supernovae (SnIa) distances is one of the primary
sources of data for cosmological models. Performing these distance estimates
involves taking a measurement of redshifted light in our observation frame and
then calculating the rest frame magnitude as if no redshift had occurred. It is
standard to report rest frame magnitudes in the $B$ filter, which is sensitive to
blue light, regardless of the filter used to take measurements in the
observation frame. The equation that converts from an observation frame
magnitude to a rest frame magnitude in the $B$ filter is called K-correction.

The first formal derivation of K-correction was performed by
\citet{tolman1930}, but it did not account for spectral bandwidth stretching,
one of the dimming effects of redshift. An alternative K-correction was
correctly derived by \citet{desitter1934}. However, in \citet{hubble1935}, the
discrepancy was noted yet dismissed. \citet{oke1968} rederived the K-correction
equation.  They accounted for spectral bandwidth stretching, but they did not
account for time dilation, one of the other dimming effects of redshift. The
paper by \citet{kim1996}, which is the basis for modern implementations of
K-correction, extended the work of \citet{oke1968} to handle additional
cross-filter comparisons and added a term that was intended to address
zero-point corrections. This history is explored in more depth in Section
\ref{sec:history}.

The effect of using an incorrect magnitude for SnIa is that we think objects
are farther away than they really are, and the effect compounds for greater
distances. Up until \citet{riess1998}, we did not have distant enough
observations for this error to matter much for cosmological models, but by the
late 1990s, it became clear that our measurements for distance and redshift were
not linear. This realization led to a model that utilized a cosmological
constant $\Lambda$ and dark energy in order to explain the non-linear
distance-redshift graph. We will show in Section \ref{sec:tension} that
correcting the flaw with K-correction leads to a linear graph that does not
need to rely on a cosmological constant.

\citet{planck2015} used an alternative technique to compute the Hubble constant
$H_0$ that is based on measurements of the cosmic microwave background (CMB).
CMB-based computations of $H_0$ has made it evident that something was missing
with our understanding of cosmology because this technique produces a
significantly different value than when the constant is derived using SnIa.  As
we will discuss in Section \ref{sec:tension}, fixing the error with
K-correction produces a measurement of the Hubble constant that is compatible
with models based on the CMB.

\section{A brief history of K-correction}
\label{sec:history}

Observational data from SnIa are essential for the calibration of models that
use redshift to estimate distance. The approximately linear relationship
between redshift and luminosity distance, often called the Hubble-Lema\^{i}tre law,
describes how quickly the universe is expanding. However, \citet{riess1998}
and \citet{perlmutter1999} presented evidence that there isn't a linear
relationship between redshift and distance, but instead, distant objects are
farther away than their redshift would predict (see Figure
\ref{fig:mu_distance_vs_redshift}). This phenomenon implies that the
acceleration of the universe is faster today than it was for old observations.
Previously the cause of this phenomenon was unknown and was referred to as dark
energy.

@@

SnIa are used to explore the relationship between distance and redshift because
these events always happen in similar ways, which keeps the absolute brightness
roughly constant. An analogy is to imagine someone walking in the dark and
lighting matches. If we know how brightly a match burns at a known distance, we
can estimate the distance to any match by measuring the apparent brightness
before applying some geometry.

@@

\begin{itemize}
  \item The energy of a wave is inversely proportional to its wavelength; thus a
  redshift of $z$ means the amount of energy per photon is reduced by a factor
  of $\frac{1}{1+z}$.

  \item The bandwidth stretches. If a rest frame observes photons
  between the wavelengths of 400nm and 401nm, then a redshift of $z = 1$
  stretches the wavelength from 800nm to 802nm.

  \item Cosmological time dilation reduces the rate at which photons arrive.
\end{itemize}

To complicate matters, we use the $B$ band magnitude to calculate luminosity
distance. We want to know how bright a supernova appears for wavelengths around
445nm as if no redshift had occurred. However, we typically need to observe the
supernova with a filter that is sensitive to longer wavelengths, such as the
$i$ band filter which is sensitive to wavelengths from 700nm-850nm
\citep{flaugher2015}. The K-correction formula allows us to take a magnitude
measured in an observation filter $y$ and compute the magnitude in the target
filter $y$.

The first mathematical treatments of K-correction was performed by
\citet{tolman1930}. However, when Tolman made his derivation, he did not
consider the effects of a spectrum that is stretched due to redshift. See
the top two panels of Figure \ref{fig:k-example} for an example of this effect.

@@

A year later, \citet{hubble1935} published a similar set of calculations for
K-correction, but these equations used $(1 + z)^2$ instead of the $(1 + z)^3$
correction term used by de Sitter. They started their derivation by copying the
incorrect equation from 1930. After their derivation, they noted:

@@

The Hubble K-correction with the incorrect correction term have been used ever
since.

By \citet{oke1968}, the two factors of $(1 + z)$ were attributed to the change
in energy and to the spectral bandwidth elongation, which leaves time dilation
as the factor that was omitted. A graph that demonstrates why it is essential to
correct for both the spectra bandwidth stretching and time dilation is presented
in Figure \ref{fig:k-example}.

\begin{figure}
  \includegraphics[width=.75\linewidth]{K-corrections_for_photon_counts.png}
  \caption{An example of how K-correction takes an observed magnitude and
  produce a rest frame magnitude. In this example, $z=1$. The observation
  filter measures magnitude, which is equivalent to measuring the number of
  photons per nanometer. In the bottom left panel, a correction of $1+z$ is
  applied which doubles the photons per nanometer. The top right panel shows
  the effect of correcting for the spectral bandwidth stretching effect --
  correcting all wavelengths for the rest frame means that the measured
  wavelengths have blueshifted, ideally into the cross band $B$ filter. Applying
  both effects, shown in the bottom right panel, requires applying two
  correction factors of $1+z$. This example omits the correction for a similar
  effect related to lower energy due to the Planck relation because CCD cameras
  obviate the need to correct for this effect.
  }
  \label{fig:k-example}
\end{figure}

The modern treatment of K-correction is based on the work of \citet{kim1996}.
This work extended the calculations of K-correction to extend to filters beyond
the blue $B$ and visible $V$ bands. It also introduced a term that deals with
the zero-point for the actual filters. In the modern day, filters measure the
photon flux as opposed to the energy flux. Historically, bolometric devices
would measure the energy flux, but modern charge-coupled device (CCD) cameras
effectively measure the photon flux.

@@

This equation has three errors that we will explore in Section
\ref{sec:consequences}.

\section{Derivation of K-correction}
\label{sec:derivation}

With modern CCD cameras, a telescope observation consists of a single value
$\mathcal{F}_x$ erg/s, which represents the energy collected in filter $x$ per
second. A summary of how this works is provided by \citet{lesser2015}.
Photogenerated electrons are collected in potential wells, which means that the
measured energy is proportional to the number of photons. However, we need to
calculate the expected number of photons collected by using a spectral energy
density function $F$. The value $F(\lambda)$ gives the amount of energy
collected by a bolometric device for the wavelength $\lambda$.

@@

It is important to note that for the blueshifted wavelength $\lambda / (1+z)$,
this equation produces

@@

  In order to account for this spectral bandwidth stretching effect, we will need
  to multiply $F'$ by a second factor of $1/(1+z)$.
\end{itemize}

Combining these two phenomena, we can calculate the redshifted spectral energy
density $R$ using

@@

Now that we have the identities in Equations \ref{eq:flux_definition} and
\ref{eq:flux2mag} we will change directions and look at the definition of
K-correction $K_{xy}$. This value allows us to make an observation in filter
$y$ and report what the magnitude would have been in filter $x$ if no redshift
occurred:

@@

\noindent The second line of Equation \ref{eq:definition} expands the distance modulus
$\mu$ using $\mu = m - M$ where $m$ is the observed magnitude and $M$ is the
absolute magnitude.

@@

It is useful to consider whether the term $\frac{P'_y}{P'_x}$ is correct or if
it should be inverted, but if we rewrite Equation \ref{eq:as_flux} as

@@

\noindent then the meaning becomes more clear. The left side, $\mathcal{F}_x
\times P'_x$, is the rate of photon collection for an idealized telescope in
filter $x$ while $\mathcal{F}_y \times P'_y$ is the rate of photon collection
for an idealized telescope in filter $y$. We observe the value $\mathcal{F}_y
\times P'_y$ and want to use the fudge factor $K'_{xy}$ to produce the value
$\mathcal{F}_x \times P'_x$.

@@

We now use Equations \ref{eq:redshifted_density} and \ref{eq:flux_definition}
to calculate the fluxes $\mathcal{F}_x$ and $\mathcal{F}_y$ in terms of the
spectral energy density function $F$. Note that $\mathcal{F}_x$ uses the rest
frame spectral energy density $F$, while $\mathcal{F}_y$ uses the redshifted
spectral energy density $R(\lambda)$:

@@

\noindent where, according to \citet{kim1996}, ``$\mathcal{Z}(\lambda)$ is an
idealized spectral energy distribution at $z = 0$ for which
$U = B = V = R = I = 0$ in the photometric system being used.'' Combining this
with Equation \ref{eq:K2k}, we have

@@

\begin{itemize}
  \item The sign is different for the first term. This will have a subtle but
  frustrating effect for real measurements. The zero-point values are usually,
  but not always, close to zero. As we observe more distant supernovae, it is
  useful to switch our observational filter to a filter that is sensitive to
  longer wavelengths. Each observation filter will have its own small bias.

  This effect by itself can alter estimates of $H_0$ by several km s$^{-1}$
  Mpc$^{-1}$.  While we present an estimate of the Hubble constant in Figure
  \ref{fig:H0bootstrap}, we are not terribly confident in the numbers because
  we were unable to correct for the zero-point errors, or verify that these
  errors may not exist.

  \item The second term is multiplied by $2.5$ in \citet{kim1996}, but is
  multiplied by $5$ here. This is the manifestation of the error in
  \citet{tolman1930}.

  \item In our derivation, the third term has an extra $1 + z$ expression.
  Based on an inspection of the SN(oo)py software package presented by
  \citet{snpy}, this error is ignored and software package authors implement it
  as intended, not precisely as written.
\end{itemize}

@@

Since the corrected values are approximately linear, we can use them to
estimate the Hubble constant $H_0$. This is demonstrated in Figure
\ref{fig:expansion}. Furthermore, we performed a bootstrap calculation to
estimate the distribution of $H_0$ estimates in Figure \ref{fig:H0bootstrap}.

The value estimated here, $H_0 \sim 65.94 \pm 1.29$ is highly suspicious
because of the flipped zero-point corrections, but it is consistent with
estimates of $H_0$ that are based on the CMB. \citet{planck2020} published the
CMB value of $H_0 \sim 67.27 \pm 0.6$, and the one sigma error bars overlap. It
is interesting to note that restricting the Dark Energy Survey observations of
SnIa \citep{vincenzi2024} to only those with $z < 0.1$, which presumably is a
small enough redshift that all observations will have been made with the same
filter, gives the estimate $H_0 \sim 67.8 \pm 1.86$.

@@

\begin{figure}
  \includegraphics[width=\linewidth]{bootstrapped_H0.png}
  \caption{A histogram of $100{\small,}000$ bootstrap trials measuring the Hubble constant
  $H_0$. Each trial samples an absolute magnitude $M \sim Norm(-19.2334,
  0.0404)$ for SnIa based on data published by \citet{camarena2020}. It then samples,
  with replacement, a population of supernovae from the dataset published by
  \citet{abbott2024}. Finally, it uses the non-parametric linear regression
  technique described by \citet{siegel1982}. The result of the bootstrap is $H_0
  \sim Norm(65.94, 1.29^2)$.
  }
\label{fig:H0bootstrap}
\end{figure}

@@

Since the K-correction error has corrupted all astronomical measurements that
depend on both magnitude and redshift, a lot of data needs to be reanalysed.
Only once the data is cleaned can cosmological parameters, such as those used
by the Friedmann-Lema\^{i}tre-Robertson-Walker (FLRW) metric or the
$\Lambda$-CDM model, be reevaluated.

The reasons that the K-correction errors went undiscovered for so long should
also be explored. Many hints existed that something was wrong, yet the
problems persisted.
